---
title: "Class 11"
author: "Katie Sanuk"
date: "2026-09-30"
output:
  html_document:
    toc: true
    toc_float: true
    number_sections: TRUE
    code_folding: show
    code_download: TRUE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Learning Objectives for Today

- Scrape multiple webpages using `for` loops;

- scrape multiple webpages using the `purrr::map()` type functions, which would also make your write your own customer functions in R.

## Extending the Course Bulletin scrape for multiple departments 

For the sake of this example. let us scrape the following pages:
[ISA](https://bulletin.miamioh.edu/courses-instruction/isa/) and
[MKT](https://bulletin.miamioh.edu/courses-instruction/mkt/) From the logic shown in class, you can essentially do that for all FSB departments.

Note that if you are doing it for just a few departments, you can just repeat your code a few times; however, this is bad practice so we will not do this in class.  Software engineers tend to refer to this as: **DRY** (don't repeat yourself).

```{r bulletin}
dept_abbr = c('acc', 'bus', 'isa', 'mkt') # extending the example to 4 dept
# line below illustrates how the url can be constructed by pasting0 (i.e., no space) the base_url, dept_abbreviation and the forward slash


courses_df = data.frame() # initialize the container
for (dept_name in (dept_abbr)) {
  cat(rep("-", 25))
  print(dept_name)
  dept_url = paste0('https://bulletin.miamioh.edu/courses-instruction/', dept_name, "/")

#for the titles, I will use the selector gadget and for the desc, I will use the inspector (to show you the alternative CSS selectors for what we did on Mon)

  webpage = rvest::read_html(dept_url)

  webpage |> rvest::html_elements("strong") |>  rvest::html_text2() -> titles
  webpage |> 
    rvest::html_elements("#sc_sccoursedescs > div > p.courseblockdesc") |> 
    rvest::html_text2() -> descs

  df = data.frame(title = titles, desc = descs)
  df$title[1] |>  print() #showing only the first course title
  
  courses_df = rbind(courses_df, df)
  cat(rep("-", 25))
}
```


## Re-examining the prior example with the `purrr` package

My preferred approach with the purrr functions is to first create my own function and then use it within the package.

```{r}
scrape_mu_bulletin = function(dept_url) {
  webpage = rvest::read_html(dept_url)

  webpage |> rvest::html_elements("strong") |>  rvest::html_text2() -> titles
  webpage |> 
    rvest::html_elements("#sc_sccoursedescs > div > p.courseblockdesc") |> 
    rvest::html_text2() -> descs

  df = data.frame(title = titles, desc = descs)
  
  return(df)
}

test=scrape_mu_bulletin("https://bulletin.miamioh.edu/courses-instruction/bus/")

dept_abbr = c('acc', 'bus', 'isa', 'mkt')
my_urls = paste0(
  "https://bulletin.miamioh.edu/courses-instruction/", #single chr string
  dept_abbr, # vector of 4 obs
  "/" #single chr string
  )

# the map functions take one or more inputs (depending on the function you are using)
#in this example, we only have 1 inpur for our function
#so we use map_() instead of map2_() [2 is if you have 2 inputs], p_map() [for 3 or more inputs]
#.x = the vector you are iterating over
courses_df_from_purrr = purrr::map_df(.x=my_urls, .f = scrape_mu_bulletin)
```

## scraping plane crash data

We will use `purrr` based on a class vote. 

```{r}
year = 2026
plane_url = paste0("https://www.planecrashinfo.com/", year, "/", year, ".htm")

webpage = rvest::read_html(plane_url)
webpage |> rvest::html_elements("center > table") |> rvest::html_table()

```

